Ordinal bhsdtr tutorial

### 2020-02-18 ordinal/Readme.Rmd
wording

Among the other problems that need to be addressed some have to do
with non-linearity and aggregation. If you fit an SDT model, or any
other non-linear model, to data aggregated over grouping factors, such
as participants or items, because of non-linearity, which does not
play well with aggregation, some or all of the point and interval
estimates may be biased, perhaps severely so, and the inference will
be invalid. You can see how horribly biased the point *and* interval
estimates of every SDT parameter may become when you overly aggregate
your data in the bhsdtr preprint. By the way, I am now in the process
of examining the direction and magnitude of bias in SDT models fitted
to overly-aggregated data by using the excellent Confidence database
created by Doby Rahnev.

>>>>

Among the other problems that need to be addressed some have to do
with non-linearity and aggregation. If you fit an SDT model, or any
other non-linear model, to data aggregated over grouping factors, such
as participants or items, because of non-linearity, which does not
play well with aggregation, some or all of the point and interval
estimates may be biased, perhaps severely so, and the inference may be
invalid. You can see how horribly biased the point *and* interval
estimates of every SDT parameter may become when you overly aggregate
your data in the bhsdtr preprint. By the way, I am now in the process
of examining the direction and magnitude of bias in SDT models fitted
to overly-aggregated data by using the excellent Confidence database
created by Doby Rahnev.
